## Clusters in cda
_baptiste Auguié -- `r format(Sys.time(), "%d %B, %Y")`_
```{r demo, message=FALSE, echo=FALSE}
knitr::read_demo("clusters", package="cda")
knitr::read_chunk("load.R")
```
```{r load, message=FALSE, echo=FALSE}
```
```{r setup, message=FALSE, echo=FALSE}
```
A cluster of particles is defined in 3 dimensions by a list with 3 components: positions of the dipoles; Euler angles to orient the polarizability tensor in space; and sizes of the particles (3 semi-axes for ellipsoids). Functions are provided for a few types of common clusters, as well as for their visualisation in 3D using OpenGl or povray.

### Manually defining a cluster
```{r manual, rgl=TRUE,echo=1:3,tidy=FALSE,fig.width=3,fig.height=3,fig.path="clusters-"}
```

### Predefined clusters

```{r dimer, rgl=TRUE,echo=1:3,tidy=FALSE,fig.width=3,fig.height=3,fig.path="clusters-"}
```

```{r chain, rgl=TRUE,echo=1:2,tidy=FALSE,fig.width=3,fig.height=3,fig.path="clusters-"}
```

```{r helix, rgl=TRUE,echo=1:4,tidy=FALSE,fig.width=3,fig.height=3,fig.path="clusters-"}
```

  