## Circular dichroism of a dimer of nanorods
_baptiste Auguié -- `r format(Sys.time(), "%d %B, %Y")`_
```{r demo, message=FALSE, echo=FALSE}
knitr::read_demo("dimer_cd", package="cda")
knitr::read_chunk("load.R")
```
```{r load, message=FALSE, echo=FALSE}
```
```{r setup, message=FALSE, echo=FALSE}
```
In this example the optical activity of a chiral dimer of axi-symmetric nanoparticles is investigated. First, we visualise the parametrisation of such a dimer with the inter-particle separation, the dihedral angle, and one additional angle for each particle.

### Cluster definition
```{r cluster, rgl=TRUE,echo=-12,tidy=FALSE,fig.width=3,fig.height=3,fig.path="dimercd-"}
```

The optical activity is modelled with full angular averaging over incident light directions. Scattering, absorption and extinction spectra are calculated for both right- and left-handed circular polarisations, and the difference corresponds to circular dichroism.

### Comparing the two mirror-images

```{r comparison,echo=TRUE,tidy=FALSE,fig.path="dimercd-",fig.width=8}
```
