In this example the optical activity of a chiral dimer of axi-symmetric nanoparticles is investigated. First, we visualise the parametrisation of such a dimer with the inter-particle separation, the dihedral angle, and one additional angle for each particle.

```{r load,message=FALSE}
library(cda)
library(rgl)
library(ggplot2)
```
```{r setup,echo=FALSE}
knit_hooks$set(rgl = function(before, options, envir) {
  # if a device was opened before this chunk, close it
  if (before && rgl.cur() > 0) rgl.close()
  hook_rgl(before, options, envir)
})
rgl_annotate = function(){
  axes3d( labels = FALSE, tick = FALSE, edges=c("x", "y", "z") )
axis3d(labels = FALSE, tick = FALSE, 'x',pos=c(NA, 0, 0))
axis3d(labels = FALSE, tick = FALSE, 'y',pos=c(0, NA, 0))
axis3d(labels = FALSE, tick = FALSE, 'z',pos=c(0, 0, NA))
title3d('','','x axis','y axis','z axis')
}
theme_set(theme_minimal())
```

### Cluster definition
```{r cluster, rgl=TRUE,echo=-12,tidy=FALSE,fig.width=3,fig.height=3,fig.path="dimercd-"}

# dielectric function
wvl <- seq(400, 900)
gold <- epsAu(wvl)

# define a dimer with dihedral angle
cl <- cluster_dimer(d=100, 
                    dihedral=45*pi/180, alpha1=10*pi/180, alpha2=0,
                    a=35, b=12)

# visualise
rgl.ellipsoids(cl$r, cl$sizes, cl$angles, col="gold")
rgl.viewpoint( theta = 0, phi = 20, fov = 70, zoom = 1)
rgl_annotate()

```

The optical activity is modelled with full angular averaging over incident light directions. Scattering, absorption and extinction spectra are calculated for both right- and left-handed circular polarisations, and the difference corresponds to circular dichroism.

### Comparing the two mirror-images

```{r comparison,echo=TRUE,tidy=FALSE,fig.path="dimercd-",fig.width=8}
  
dimer <- function(dihedral=45, ...){
  cl <- cluster_dimer(dihedral = dihedral * pi/180, ...)
  circular_dichroism_spectrum(cl, material = gold)
  
}
params <- data.frame(dihedral=c(45, 30, 10, 0, -10, -30,-45),
                     d=100, a=35, b=12, 
                     alpha1=10*pi/180, alpha2=0)
comparison <- mdply(params, dimer)

p <- 
  ggplot(data=comparison) + 
  facet_grid(type~variable, scales="free") +
  geom_line(aes(wavelength, value, 
                colour=factor(dihedral))) +
  labs(y=expression(sigma[ext]*" /"*nm^2),
       x=expression(wavelength*" /"*nm), colour="dihedral angle") +
         scale_colour_brewer(type="div", palette=3)

p
```
